Flexibility of interactions depends on habitat suitability

### 2019-09-14 paper/manuscript.Rmd
Another paragraph to the discussion

* Add in the intro that stress includes how traits mediate environment?
* Why is the relationship different across species?
* Why is there no difference between plants and pollinators?
* Why is there a correlation between the intercept and the slope?
* The environment can certainly influence the number of interactions but its very variable among species
* In the absence of abundance this is as much as we can say. 
* It is remarkable we found a signal given the amount of data we had it is realy not that much for our question. It is not surprising that the slope of suitability was small for many species as we had little data. The results hold for when species had
* Implications for community assembly and network rewiring.

>>>>

These observations have implications for understanding the assembly of ecological networks and how it might be impacted by climate change, which currentlt threatens to increasse the environmental stress of species within its range. 
Previous research suggests that flexibility of interactions in ecological communities might be a rather ubiquitous phenomenon whenever environemntal conditions change in space or time [@caradonna_interaction_2017]. 
This flexibility has been shown to confer robustness and stability to the loss of interaction partners [@kaiser-bunbury_robustness_2010]. 
The current paradigm of interaction turnover suggest first that trait matching is a relatively unimportant driver of interaction turnover for generalist species [@caradonna_interaction_2017]. 
The fact that species with a high number of interactions were more likely to interact with less species as environmental stress increassed indicates that trait matching might still play a role at determining the interactions of generalist species. 
Second, current research suggests that the rewiring of the interaction network is primarly driven by generalist species [@burkle_plant-pollinator_2013].
We, however, demonstrate that at least a fraction of the species that appear to be specialist in their communities might be more flexible, if not more, than generalist species and, therefore, might a larger role in network persistence than previously expected. 
Contrastingly, specialists that are highly constrained to interact with partners of high trait-matching might be more vulnerable to increassed climate change induced environmental stress and habitat degradation. 
Taken together, the fact that most species appear to be flexible interaction partners, combined with the fact that those that are not flexible are less likely to persist, might expain why specialised communities that are highly constrained by trait matching [like some plant-humingbird networks; @vizentin-bugoni_processes_2014; @maruyama_morphological_2014] might be relatively rare.

In conclusion, we show that

It still remains to evaluate the role of abundance and neutral processes and

* Add in the intro that stress includes how traits mediate environment?
* Why is the relationship different across species?
* The environment can certainly influence the number of interactions but its very variable among species
* In the absence of abundance this is as much as we can say. 
* It is remarkable we found a signal given the amount of data we had it is realy not that much for our question. It is not surprising that the slope of suitability was small for many species as we had little data. The results hold for when species had
* Implications for community assembly and network rewiring.
